Active Learning for Level Set Estimation

### 2013-03-23 figurefactory/files/ev_bgape_eps.tex
More fixes and reductions

\begin{axis}[%
tick label style={font=\tiny},
label style={font=\tiny},
xlabel shift={-6pt},
ylabel shift={-4pt},
legend style={font=\tiny},
view={0}{90},
width=\figurewidth,
height=\figureheight,
scale only axis,
xmin=0, xmax=400,
xlabel={Samples},
ymin=0.5, ymax=1,
ylabel={$F_1$-score},
name=plot1,
axis lines*=left,
colormap={mymap}{[1pt] rgb(0pt)=(0.5,0,0); rgb(8pt)=(1,0,0); rgb(24pt)=(1,1,0); rgb(40pt)=(0,1,1); rgb(56pt)=(0,0,1); rgb(63pt)=(0,0,0.5625)},
colorbar right,
colorbar style={
  tickwidth=0.03cm,
  at={(1.06, 0)},
  anchor=south east,
  yticklabel pos=right,
  yticklabel shift={-2pt}
},
tickwidth=0.1cm,
colorbar/width=0.15cm,
point meta min=0,
point meta max=2
]

>>>>

\begin{axis}[%
tick label style={font=\scriptsize},
label style={font=\scriptsize},
label shift={-4pt},
xlabel shift={-6pt},
legend style={font=\scriptsize},
view={0}{90},
width=\figurewidth,
height=\figureheight,
scale only axis,
xmin=0, xmax=400,
xlabel={Samples},
ymin=0.5, ymax=1,
ylabel={$F_1$-score},
name=plot1,
axis lines*=left,
colormap={mymap}{[1pt] rgb(0pt)=(0.5,0,0); rgb(8pt)=(1,0,0); rgb(24pt)=(1,1,0); rgb(40pt)=(0,1,1); rgb(56pt)=(0,0,1); rgb(63pt)=(0,0,0.5625)},
colorbar right,
colorbar style={
  tickwidth=0.03cm,
  at={(1.06, 0)},
  anchor=south east,
  yticklabel pos=right,
  yticklabel shift={-2pt}
},
tickwidth=0.1cm,
colorbar/width=0.15cm,
point meta min=0,
point meta max=2
]

### 2013-03-23 figurefactory/files/ev_chl_eps.tex
More fixes and reductions

\begin{axis}[%
tick label style={font=\tiny},
label style={font=\tiny},
xlabel shift={-6pt},
ylabel shift={-4pt},
legend style={font=\tiny},
view={0}{90},
width=\figurewidth,
height=\figureheight,
scale only axis,
xmin=0, xmax=400,
xlabel={Samples},
ymin=0.5, ymax=1,
ylabel={$F_1$-score},
name=plot1,
axis lines*=left,
colormap={mymap}{[1pt] rgb(0pt)=(0.5,0,0); rgb(8pt)=(1,0,0); rgb(24pt)=(1,1,0); rgb(40pt)=(0,1,1); rgb(56pt)=(0,0,1); rgb(63pt)=(0,0,0.5625)},
colorbar right,
colorbar style={
  tickwidth=0.03cm,
  at={(1.06, 0)},
  anchor=south east,
  yticklabel pos=right,
  yticklabel shift={-2pt}
},
tickwidth=0.1cm,
colorbar/width=0.15cm,
point meta min=0,
point meta max=1
]

>>>>

\begin{axis}[%
tick label style={font=\scriptsize},
label style={font=\scriptsize},
label shift={-4pt},
xlabel shift={-6pt},
legend style={font=\scriptsize},
view={0}{90},
width=\figurewidth,
height=\figureheight,
scale only axis,
xmin=0, xmax=400,
xlabel={Samples},
ymin=0.5, ymax=1,
ylabel={$F_1$-score},
name=plot1,
axis lines*=left,
colormap={mymap}{[1pt] rgb(0pt)=(0.5,0,0); rgb(8pt)=(1,0,0); rgb(24pt)=(1,1,0); rgb(40pt)=(0,1,1); rgb(56pt)=(0,0,1); rgb(63pt)=(0,0,0.5625)},
colorbar right,
colorbar style={
  tickwidth=0.03cm,
  at={(1.06, 0)},
  anchor=south east,
  yticklabel pos=right,
  yticklabel shift={-2pt}
},
tickwidth=0.1cm,
colorbar/width=0.15cm,
point meta min=0,
point meta max=1
]

### 2013-03-23 msthpres.tex
More fixes and reductions

\begin{frame}
\begin{itemize}
\item<1-> Pose as a sequential decision making problem (\emph{pool-based active learning}):
\begin{itemize}
\item<2-> No measurements available in advance, just a set (pool) of possible sampling locations ($D$)
\vspace{0.5em}
\item<3->[]\hspace{-1.5em} At each iteration $t \geq 1$:
\item<3-> Decide where to measure next ($x_t$)
\item<4-> Obtain noisy observation ($y_t = f(x_t) + n_t$)
\item<5-> Update our estimate of the underlying function (e.g. algae concentration)
\end{itemize}
\end{itemize}
\begin{center}
\color{white}
\includegraphics<1>[draft,width=4.45in]{figures/oned_0}
\color{black}
\includegraphics<2>[width=4.45in]{figures/oned_0}
\includegraphics<3>[width=4.45in]{figures/oned_1_0}
\includegraphics<4>[width=4.45in]{figures/oned_1_1}
\includegraphics<5>[width=4.45in]{figures/oned_1_2}
\includegraphics<6>[width=4.45in]{figures/oned_2_0}
\includegraphics<7>[width=4.45in]{figures/oned_2_1}
\includegraphics<8>[width=4.45in]{figures/oned_2_2}
\end{center}
\end{frame}

@@

\begin{frame}
\begin{itemize}
\item<1-> What if we don't know $h$?
\item<2-> Implicitly define the threshold level: $h = \omega \max_{\*x\in D} f(\*x),\ 0 < \omega < 1$
\item<5-> \iacl:
\begin{itemize}
\item<5-> Need to accurately estimate the maximum (don't exclude points that could be maximizers)
\item<6-> Slower classification
\end{itemize}
\end{itemize}
\begin{center}
\color{white}
\only<1-2>{\includegraphics[draft,width=3.77in]{figures/voned_cl_41_imp_1}}
\color{black}
\only<3>{\includegraphics[width=3.77in]{figures/voned_cl_41_imp_1}}
\only<4->{\includegraphics[width=3.77in]{figures/voned_cl_41_imp_2}}
\end{center}
\end{frame}

@@

\begin{frame}
\begin{center}
\includegraphics[width=2.3in]{figures/ev_chl_imp}
\includegraphics[width=2.3in]{figures/ev_bgape_imp}
\end{center}
\end{frame}

@@

\begin{center}
\color{white}
\includegraphics<1-3>[draft,width=3.78in]{figures/limno_bgape_pp_0_0}
\color{black}
\includegraphics<4>[height=1.8in]{figures/limno_bgape_pp_0_0}
\includegraphics<5>[height=1.8in]{figures/limno_bgape_pp_0_1}
\includegraphics<6>[height=1.8in]{figures/limno_bgape_pp_0_2}
\includegraphics<7>[height=1.8in]{figures/limno_bgape_pp_30_0}
\includegraphics<8>[height=1.8in]{figures/limno_bgape_pp_30_1}
\includegraphics<9>[height=1.8in]{figures/limno_bgape_pp_30_2}
\includegraphics<10>[height=1.8in]{figures/limno_bgape_pp_60_0}
\includegraphics<11>[height=1.8in]{figures/limno_bgape_pp_60_1}
\includegraphics<12>[height=1.8in]{figures/limno_bgape_pp_60_2}
\includegraphics<13>[height=1.8in]{figures/limno_bgape_pp_90_0}
\includegraphics<14>[height=1.8in]{figures/limno_bgape_pp_90_1}
\includegraphics<15>[height=1.8in]{figures/limno_bgape_pp_90_2}
\includegraphics<16>[height=1.8in]{figures/limno_bgape_pp_120_0}
\includegraphics<17>[height=1.8in]{figures/limno_bgape_pp_120_1}
\includegraphics<18>[height=1.8in]{figures/limno_bgape_pp_120_2}
\includegraphics<19>[height=1.8in]{figures/limno_bgape_pp_150_0}
\includegraphics<20>[height=1.8in]{figures/limno_bgape_pp_150_1}
\includegraphics<21>[height=1.8in]{figures/limno_bgape_pp_150_2}
\includegraphics<22>[height=1.8in]{figures/limno_bgape_pp_180_0}
\includegraphics<23>[height=1.8in]{figures/limno_bgape_pp_180_1}
\includegraphics<24>[height=1.8in]{figures/limno_bgape_pp_180_2}
\includegraphics<25>[height=1.8in]{figures/limno_bgape_pp_210_0}
\includegraphics<26>[height=1.8in]{figures/ev_bgape_pp}
\end{center}
\end{frame}

>>>>

\begin{frame}
\begin{itemize}
\item<1-> Pose as a sequential decision making problem (\emph{pool-based active learning}):
\begin{itemize}
\item<2-> No measurements available in advance, just a set (pool) of possible sampling locations ($D$)
\vspace{0.5em}
\item<3->[]\hspace{-1.5em} At each iteration $t \geq 1$:
\item<3-> Decide where to measure next ($x_t$)
\item<4-> Obtain noisy observation ($y_t = f(x_t) + n_t$)
\item<5-> Update our estimate of the underlying function
\end{itemize}
\end{itemize}
\begin{center}
\color{white}
\includegraphics<1>[draft,width=4.45in]{figures/oned_0}
\color{black}
\includegraphics<2>[width=4.45in]{figures/oned_0}
\includegraphics<3>[width=4.45in]{figures/oned_1_0}
\includegraphics<4>[width=4.45in]{figures/oned_1_1}
\includegraphics<5>[width=4.45in]{figures/oned_1_2}
\includegraphics<6>[width=4.45in]{figures/oned_2_0}
\includegraphics<7>[width=4.45in]{figures/oned_2_1}
\includegraphics<8>[width=4.45in]{figures/oned_2_2}
\end{center}
\end{frame}

@@

\begin{frame}
\begin{itemize}
\item<1-> What if we don't know $h$?
\vspace{1em}
\item<2-> Implicitly define the threshold level: $h = \omega \max_{\*x\in D} f(\*x),\ 0 < \omega < 1$
\vspace{1em}
\item<3-> \iacl:
\begin{itemize}
\item<4-> Need to also estimate the maximum
\item<5-> Slower classification due to uncertainty about $h$
\end{itemize}
\end{itemize}
\begin{center}
%\color{white}
%\only<1-2>{\includegraphics[draft,width=3.77in]{figures/voned_cl_41_imp_1}}
%\color{black}
%\only<3>{\includegraphics[width=3.77in]{figures/voned_cl_41_imp_1}}
%\only<4->{\includegraphics[width=3.77in]{figures/voned_cl_41_imp_2}}
\end{center}
\end{frame}

@@

%\begin{frame}
%\begin{center}
%\includegraphics[width=2.3in]{figures/ev_chl_imp}
%\includegraphics[width=2.3in]{figures/ev_bgape_imp}
%\end{center}
%\end{frame}

@@

\begin{center}
\color{white}
\includegraphics<1-3>[draft,height=1.8in]{figures/limno_bgape_pp_0_0}
\color{black}
\includegraphics<4>[height=1.8in]{figures/limno_bgape_pp_0_0}
\includegraphics<5>[height=1.8in]{figures/limno_bgape_pp_0_1}
\includegraphics<6>[height=1.8in]{figures/limno_bgape_pp_0_2}
\includegraphics<7>[height=1.8in]{figures/limno_bgape_pp_30_0}
\includegraphics<8>[height=1.8in]{figures/limno_bgape_pp_30_1}
\includegraphics<9>[height=1.8in]{figures/limno_bgape_pp_30_2}
\includegraphics<10>[height=1.8in]{figures/limno_bgape_pp_60_0}
\includegraphics<11>[height=1.8in]{figures/limno_bgape_pp_60_1}
\includegraphics<12>[height=1.8in]{figures/limno_bgape_pp_60_2}
\includegraphics<13>[height=1.8in]{figures/limno_bgape_pp_90_0}
\includegraphics<14>[height=1.8in]{figures/limno_bgape_pp_90_1}
\includegraphics<15>[height=1.8in]{figures/limno_bgape_pp_90_2}
\includegraphics<16>[height=1.8in]{figures/limno_bgape_pp_120_0}
\includegraphics<17>[height=1.8in]{figures/limno_bgape_pp_120_1}
\includegraphics<18>[height=1.8in]{figures/limno_bgape_pp_120_2}
\includegraphics<19>[height=1.8in]{figures/limno_bgape_pp_150_0}
%\includegraphics<20>[height=1.8in]{figures/limno_bgape_pp_150_1}
%\includegraphics<21>[height=1.8in]{figures/limno_bgape_pp_150_2}
%\includegraphics<22>[height=1.8in]{figures/limno_bgape_pp_180_0}
%\includegraphics<23>[height=1.8in]{figures/limno_bgape_pp_180_1}
%\includegraphics<24>[height=1.8in]{figures/limno_bgape_pp_180_2}
%\includegraphics<25>[height=1.8in]{figures/limno_bgape_pp_210_0}
\includegraphics<20>[height=1.8in]{figures/ev_bgape_pp}
\end{center}
\end{frame}
